### 2020-06-03 Documents/ChaoticDynamics/WriteUp.tex
Added Results to Chaotic Dynamics

\usepackage[margin=2cm]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}

\usepackage{color}
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}

@@

% section stability_analysis (end)
\end{document}

>>>>

\usepackage[margin=2cm]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}

@@

% section stability_analysis (end)

\section{Numerical Simulations} % (fold)
\label{sec:numerical_simulations}

\begin{figure}[h]

	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\end{subfigure}

	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
	converged based on a tolerance of 1\% difference between action probabilities. For each
	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
	and initial conditions. The average number of converged games (giving an indication of
	probability of convergence) is shown in each cell of the heatmap.}
\end{figure}

% section numerical_simulations (end)
\end{document}

### 2020-06-03 Documents/ESA/sections/Intro.tex
Added Results to Chaotic Dynamics

>>>>

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{HammanFormalApproach}. The union of populations of
    agents who share the same goal can give rise to behaviours that are far more complex than
    individual robots can achieve. The same, of course, is true for humans; whilst an individual may
    be capable of building a house, it takes many more to build a city.

    The ability to exhibit complex
